A point-level trend model for the North American Breeding Bird Survey that corrects for detectability

### 2023-07-14 article/article.tex
small updates to next steps section

>>>>

\section{Next Analysis Steps}
\subsection{Develop Model Code}
Given Equation \ref{bbs_varprop}, the next steps would be to write this model in Stan. This can likely be done relatively quickly as the spatially explicit base model is available through the R package \textit{bbsBayes2} \citep{edwards_bbsbayes_2021}, and so this pre-existing model file can easily be modified to include the above effects and offset.

\subsection{Test Model}
